\section{Purpose}
\label{sec:purpose}%
The Students \& Companies (S\&C) platform was created by a different team as a component of the Software Engineering 2 course, and the Acceptance Test Document (ATD) attempts to verify and methodically test its implementation. This document guarantees that the project satisfies the requirements listed in the Design Document (DD) and the Requirement Analysis and Specification Document (RASD). Verifying essential features, identifying discrepancies, and assessing how well the system satisfies user requirements and expected behaviors are the main goals of the testing process.


\section{Scope}
\label{subsec:scope}%
\newcounter{g}
\setcounter{g}{1}
\newcommand{\cg}{\theg\stepcounter{g}}

The Students \& Companies (S\&C) platform is designed to facilitate internship opportunities for students by connecting them with potential recruiters and enabling universities to monitor student internships. The platform includes the following key functionalities:
\begin{itemize}
    \item \textbf{Internship Lookup for Students:} Depending on their preferences, education, and skill set, students might look for and apply for internships.
    \item \textbf{Visibility for Companies:} Recruiters can post internship openings and match qualified student profiles with them.
    \item \textbf{Selection Process Management:} Employers are able to manage selections, set up interviews, and evaluate student applications.
    \item \textbf{Recommendation System:} Makes individualized internship recommendations using user data and gathered statistics.
     \item \textbf{Communication \& Feedback:} Allows for message sharing, problem reporting, and post-internship feedback between students and businesses.
     \item \textbf{University Monitoring:} To guarantee academic compliance, universities might supervise their students' internships.
\end{itemize}

The S\&C platform was developed by:
\begin{itemize}
    \item Edoardo S. Gribaldo
    \item Federico Rosa
\end{itemize}

The GitHub repository for the project can be found here: \href{https://github.com/edogriba/GribaldoRosa}{S\&C Repository}

\section{Revision History}
\label{sec:revision_history}

\begin{table}[H]
    \centering
    \begin{tabular}{ |p{0.1\linewidth}|p{0.15\linewidth}|p{0.45\linewidth}|p{0.2\linewidth}| }
        \hline
        \textbf{Version} & \textbf{Date} & \textbf{Description} & \textbf{Authors} \\
        \hline
        1.0 & 06 February 2025 & Initial Release & 
        Shreesh Kumar Jha, \newline
        Samarth Bhatia \\
        \hline
    \end{tabular}
    \caption{Revision History}
    \label{tab:revision_history}
\end{table}

\section{Reference Documents}
\label{sec:reference_documents}%
\begin{itemize}
    \item Reference to Previous Year Student Projects for Structuring the Document
    \item \href{https://github.com/edogriba/GribaldoRosa/blob/main/DeliveryFolder/RASDv1.pdf}{\textbf{\textcolor{blue}{\underline{RASDv1}}}}
    \item \href{https://github.com/edogriba/GribaldoRosa/blob/main/DeliveryFolder/ITDv1.pdf}{\textbf{\textcolor{blue}{\underline{ITDv1}}}}
    \item \href{https://github.com/edogriba/GribaldoRosa/blob/main/DeliveryFolder/DDv1.pdf}{\textbf{\textcolor{blue}{\underline{DDv1}}}}
\end{itemize}

\section{Document Structure}
\label{sec:document_structure}%
This document is structured as follows:

\subsection*{Installation Setup}
\begin{itemize}
    \item Details the steps followed to install and test the S\&C platform.
    \item Highlights any encountered issues, inconsistencies, or missing documentation.
\end{itemize}

\subsection*{Acceptance Test Cases}
\begin{itemize}
    \item Describes the test cases executed against the system.
    \item Maps tests to system requirements and goals as outlined in the \texttt{RASDv1}, \texttt{DDv1}, and \textttt{ITDv1}.
    \item Documents observed results, including any failures and potential fixes.
\end{itemize}

