\section{System Requirements}
\label{sec:system_requirements}

This section outlines the functional requirements of the InternHub – Students \& Companies (S\&C) platform, categorized by the major system components.

\subsection{Login Manager}
\label{subsec:login_manager}
\begin{enumerate}[label=R\arabic*:, itemsep=0.2em]
    \item The system allows registered students to log in.
    \item The system allows registered companies to log in.
    \item The system ensures secure access to accounts through credential verification.
    \item The system validates user input during login.
    \item The system provides error messages for invalid credentials.
\end{enumerate}

\subsection{Registration Manager}
\label{subsec:registration_manager}
\begin{enumerate}[label=R\arabic*:, itemsep=0.2em, start=6]
    \item The system allows unregistered users (students and companies) to sign up.
    \item The system verifies user details before creating accounts.
    \item The system communicates with the mailing system to send verification emails during registration.
    \item The system ensures unique email addresses during registration.
    \item The system allows recruiters to register company profiles with required information fields.
\end{enumerate}

\subsection{Internship Manager}
\label{subsec:internship_manager}
\begin{enumerate}[label=R\arabic*:, itemsep=0.2em, start=11]
    \item The system allows companies to create new internship postings.
    \item The system allows companies to update existing internship details.
    \item The system enables recruiters to delete internships.
    \item The system fetches all internship postings associated with a specific recruiter.
    \item The system provides students with the ability to search and filter internships based on preferences.
    \item The system supports adding multiple job roles under a single internship posting.
    \item The system tracks the total number of internships posted by a company.
\end{enumerate}

\subsection{Application Manager}
\label{subsec:application_manager}
\begin{enumerate}[label=R\arabic*:, itemsep=0.2em, start=18]
    \item The system allows students to submit applications for internships.
    \item The system enables recruiters to review student applications.
    \item The system tracks the status of submitted applications.
    \item The system supports updating the status of an application (e.g., accepted, rejected).
    \item The system provides recruiters with filters to search through applications.
    \item The system notifies students of changes in their application status.
\end{enumerate}

\subsection{Interview Manager}
\label{subsec:interview_manager}
\begin{enumerate}[label=R\arabic*:, itemsep=0.2em, start=24]
    \item The system allows recruiters to schedule interviews for shortlisted candidates.
    \item The system notifies students of upcoming interviews.
    \item The system tracks interview details and schedules.
    \item The system sends reminders to students and recruiters for scheduled interviews.
    \item The system allows students to view interview details, including time and interviewer.
    \item The system supports rescheduling of interviews by recruiters.
\end{enumerate}

\subsection{Complaint Manager}
\label{subsec:complaint_manager}
\begin{enumerate}[label=R\arabic*:, itemsep=0.2em, start=30]
    \item The system allows users (students and companies) to file complaints regarding issues.
    \item The system ensures proper logging of all complaints for administrative review.
    \item The system enables administrators to resolve complaints and update their status.
    \item The system notifies users about updates to their complaints.
    \item The system maintains a history of resolved complaints for audit purposes.
\end{enumerate}

\subsection{Profile Manager}
\label{subsec:profile_manager}
\begin{enumerate}[label=R\arabic*:, itemsep=0.2em, start=35]
    \item The system allows students to manage their profiles, including uploading resumes and updating details.
    \item The system allows companies to manage their profiles and update organization details.
    \item The system supports the ability to view profiles of other users (students or companies).
    \item The system provides recommendations for internships based on student profiles.
    \item The system highlights incomplete profiles for users and prompts them to complete missing details.
\end{enumerate}

\subsection{Search and Filter}
\label{subsec:search_and_filter}
\begin{enumerate}[label=R\arabic*:, itemsep=0.2em, start=40]
    \item The system provides students and companies with advanced search and filter options for internships, candidates, or postings.
    \item The system ensures search results are relevant and aligned with user preferences.
    \item The system supports search by location, duration, stipend, and skills.
    \item The system allows recruiters to filter student applications by skills and experience.
    \item The system enables sorting of search results by relevance or other criteria.
\end{enumerate}

\subsection{Dashboard Manager}
\label{subsec:dashboard_manager}
\begin{enumerate}[label=R\arabic*:, itemsep=0.2em, start=45]
    \item The system provides students with an overview of their active applications, upcoming interviews, and recent internship matches.
    \item The system provides companies with an overview of active postings, total applicants, and scheduled interviews.
    \item The system allows administrators to monitor platform activities, including user engagement and complaint handling.
    \item The system displays key metrics for students, such as total applications and new messages.
    \item The system allows companies to see statistics on applicants and hires.
\end{enumerate}

\subsection{Notification Manager}
\label{subsec:notification_manager}
\begin{enumerate}[label=R\arabic*:, itemsep=0.2em, start=50]
    \item The system sends notifications to students when their application status is updated.
    \item The system notifies students and companies of scheduled interviews.
    \item The system sends reminders for upcoming deadlines, including applications and interviews.
    \item The system notifies users about updates to their complaints.
    \item The system alerts students about new internship matches based on their profiles.
\end{enumerate}

\subsection{Model}
\label{subsec:model}
\begin{enumerate}[label=R\arabic*:, itemsep=0.2em, start=55]
    \item The system securely stores user data, including profiles, applications, and complaints.
    \item The system ensures the integrity and security of all data through encryption and access controls.
    \item The system logs all user actions for security and audit purposes.
    \item The system supports scalable storage for managing increasing user data.
    \item The system ensures efficient data retrieval for dashboard and search functionalities.
\end{enumerate}
